Corpus

### 2020-05-15 evaluation/R/corpus.Rmd

@@

@@

```{r joining data}
pkgs <-
  pkgs_cran %>%
  left_join(mutate(pkgs_installed, installed=TRUE), by="package") %>% mutate(installed=replace_na(installed, FALSE)) %>%
  left_join(transmute(pkgs_loadable, package, loadable=TRUE), by="package") %>% mutate(loadable=replace_na(loadable, FALSE)) %>%
  left_join(pkgs_metadata, by="package") %>%
  left_join(pkgs_sloc, by="package") %>%
  left_join(pkgs_runnable_code, by="package") %>%
  left_join(pkgs_coverage, by="package") %>%
  left_join(pkgs_runs, by="package") %>%
  left_join(pkgs_functions, by="package") %>%
  left_join(pkgs_classes, by="package") %>%
  left_join(pkgs_revdeps, by="package") %>%
  left_join(pkgs_asserts, by="package") %>%
  left_join(pkgs_roxygen, by="package")
```

>>>>

```{r}
pkgs_coverage_funs <-
  filter(coverage_funs, coverage > 0) %>%
  count(package) %>%
  rename(funs_with_coverage=n)
```

@@

```{r}
pkgs_revdeps_coverage <- 
  read_csv(
    PACKAGE_REVDEPS_COVERAGE,
    col_types=cols(
      package = col_character(),
      revdep_coverage_expression = col_double(),
      revdep_coverage_line = col_double(),
      n_revdeps = col_double(),
      n_ran_revdeps = col_double()
    )
  ) %>%
  select(
    package,
    revdep_coverage_expr=revdep_coverage_expression,
    revdep_coverage_line,
    revdep_coverage_runs=n_ran_revdeps
  )
```

@@

```{r joining data}
pkgs <-
  pkgs_cran %>%
  left_join(mutate(pkgs_installed, installed=TRUE), by="package") %>% mutate(installed=replace_na(installed, FALSE)) %>%
  left_join(transmute(pkgs_loadable, package, loadable=TRUE), by="package") %>% mutate(loadable=replace_na(loadable, FALSE)) %>%
  left_join(pkgs_metadata, by="package") %>%
  left_join(pkgs_sloc, by="package") %>%
  left_join(pkgs_runnable_code, by="package") %>%
  left_join(pkgs_coverage, by="package") %>%
  left_join(pkgs_coverage_funs, by="package") %>%
  left_join(pkgs_runs, by="package") %>%
  left_join(pkgs_functions, by="package") %>%
  left_join(pkgs_classes, by="package") %>%
  left_join(pkgs_revdeps, by="package") %>%
  left_join(pkgs_asserts, by="package") %>%
  left_join(pkgs_roxygen, by="package")
```
